### 2019-06-13 2-Chapters/6-Chapter/nonstatbandits.git/NonStatB.tex
Lots of small changes. I'll start fixing Chapter 2 this weekend, today my goal is Ch1
Better links to
- https://SMPyBandits.GitHub.io/MultiPlayers.html
- https://SMPyBandits.GitHub.io/NonStationaryBandits.html

\paragraph{A note on the simulation code.}
%
All the experiments used for this chapter were performed using SMPyBandits,
and we refer to the following page for details on how to reproduce them,
\href{https://SMPyBandits.GitHub.io/NonStationaryBandits.html}{\texttt{SMPyBandits.GitHub.io/NonStationaryBandits.html}}

>>>>

% \paragraph{A note on the simulation code.}
\paragraph{Reproducility of the experiments.}
%
The experiments in this chapter use our library SMPyBandits, as presented in Chapter~\ref{chapter:3},
and we refer to the following page for details on how to reproduce them,
\href{https://SMPyBandits.GitHub.io/NonStationaryBandits.html}{\texttt{SMPyBandits.GitHub.io/NonStationaryBandits.html}}
